Thermal relaxation is important in convective simulations: \\ on the time evolution of flows and how to avoid unnecessary thermal rundown

### 2020-01-18 tex/mixedft_evolution_ms.tex
rough draft of paper complete

\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography]{revtex4-1}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

@@

\title{Mixed thermal boundary conditions impose an unnecessary thermal rundown on convection simulations}

@@

\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
Numerical simulations are the basis for most modern studies into the nature of astrophysical convection.
Some modern studies examine convection in the highly simplified Boussinesq approximation \cite{spiegel&veronis1960}.
Others study more complex ``dynamo simulations'', incorporating complicating effects such as magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
Regardless of the degree of apparent realism included in these models, convective processes in these numerical simulations are fundamentally driven by some combination of imposed boundary conditions and internal heating profiles which in turn determine key properties of the evolved dynamics \cite{goluskin2015}.
In astrophysical studies, a common choice of thermal boundary conditions \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection under the Boussinesq approximation.
In this model, the only thermodynamic quantity of interest is the temperature, and we will hereafter refer to this choice of boundary conditions (fixed flux at the bottom, fixed temperature at the top) as ``mixedFT'' boundaries.

Despite mixedFT boundary conditions being a common choice of numericists, we are unaware of any work which compares the dynamics produced by mixed thermal boundaries to the most traditional choice of boundary conditions in the \RB literature: fixed temperature at the top and bottom (hereafter ``fixedT'' boundaries).
Due to the fact that mixedFT boundaries fix the flux through the convective system, this set of boundaries is expected to behave in a fundamentally similar way to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
While there is some work \cite{johnston&doering2009} comparing fixedF and fixedT boundaries, past work primarily focused on the scaling of heat transport laws (quantified by a Nusselt number, Nu) as the convective driving is increased (quantified by the Rayleigh number, Ra) [more refs].
The equivalence of fixedF and fixedT scaling laws suggests that mixedFT scaling should also be identical.
However, the choice of mixedFT boundaries introduces complexities into the convective system which neither fixedF or fixedT boundaries are exposed to.
First, the evolved mean temperature of a simulation with mixedFT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
Second, mixedFT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.

In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
We also find that this rapid thermal evolution can be bypassed by combining the results of fixedT and mixedFT simulations.
We furthermore find that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not seem to appreciably change the mean convective state when compared to fixedT boundaries, even when the Rayleigh number is large.
We present these findings as follows.
In section \ref{sec:simulations}, we describe our experimental setup and numerical methods.
In section \ref{sec:results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
In section \ref{sec:rotating_results}, we briefly show that these findings carry over to a more complex system: rotating \RB convection.
Finally, in section \ref{sec:discussion}, we briefly describe the implications of this work for the field of astrophysical convection.

@@

\section{Simulation Details}
\label{sec:simulations}
We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so we include it here for generality.
The equations of motion are
\begin{align}
\Div{\bm{u}} &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \sqrt{\frac{\nu}{2\Omega L_z^2}},
\end{equation}
where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency.
These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
$\Delta$ is the dimensionless temperature jump across the domain; depending on our choice of boundary condition, $\Delta$ defines either a temperature or flux Rayleigh number,
\begin{equation}
\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
\end{equation}
We study both mixedFT and fixedT thermal boundary conditions,
\begin{equation}
(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\&\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
(\text{fixedT}): T_1 = 0 \text{ at $z$ = -0.5, 0.5}.
\end{equation}
In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.

Throughout the bulk of this work, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}
The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset, as has been done by previous authors \cite{stellmach&all2014}. 
These rotating simulations employ stress-free, impenetrable boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}

We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}. 
The code used to run simulations and the code and data used to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
We fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT simulation (green) and a fixedT (orange) simulation.
	(top left panel) The Rayleigh number, normalized by the input Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$ value of the mixedFT simulation.
	(middle and bottom left panels) The Nusselt number and Peclet number evolution of the simulations is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation.
	(right two panels) Parameter space plots of Nusselt (upper) and Peclet (lower) vs. Ra$_{\Delta T}$.
	The green traces show the time evolution of the mixedFT case, while the orange circles and black crosses show comparison fixedT simulations.
	The orange star in each plot corresponds to the fixedT case whose time evolution is shown on the left.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a mixedFT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
This simulation had a coefficient resolution of (nz, nx) = (1024, 2048) and was evolved forward in time for ten days on 512 cpus.
The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$, with a coefficient resolution of (nz, nx) = (512, 1024) which was time evolved for one thousand freefall time units after the initial convective transient (which took roughly one day on 256 cpus).
The mixedFT case is displayed in green, and the fixedT case is displayed in orange; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the mixedFT simulation, and this final value corresponds to the input value of the equivalent fixedT case.
On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reaches its final value, which corresponds to the input value for the mixedFT simulation.
This discrepancy in evolution timescales, where fixedT simulations evolve quickly and mixedFT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.

In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot Nu and Pe vs Ra$_{\Delta T}$.
The green line shown in each panel is the path through parameter space that the mixed-FT simulation traces out over its time evolution.
In the upper right (Nu vs Ra) plot, we have divided all Nu values by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by \cite{johnston&doering2009}.
In the lower right (Re vs Ra) plot, we have divided out a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
The orange circles show the mean values of Nu and Pe from select fixedT simulations through this parameter space, the details of which are presented in appendix \ref{app:table}; in all cases, we plot the sample mean, and the standard deviation of the sample mean is smaller than the plotted points.
The orange star is the simulation whose time evolution is shown on the left.
The black crosses are the reported values of Nu from the supplemental materials of \cite{zhu&all2018}, presented for comparison.
Remarkably, the mixedFT case seems to reliably perform a sweep through this parameter space.
However, despite seemingly tracing out the ``proper'' values of Nu(t) vs. Ra$_{\Delta T}$(t), we find that the mixedFT simulation achieves a larger value of the Peclet number than the comparison fixedT simulations until it converges to its final state.
These traces through parameter space help to demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
	The mean value of the simulation's temperature gradient (middle panel) and temperature (bottom panel) are displayed, showing the change in the enforced boundary condition.
	In the middle panel, during the fixedT portion of the simulation, we plot $\angles{Nu}\partial_z T$, while in the bottom panel, during the mixedFT portion, we plot $T / \angles{Nu}$ due to the change in temperature nondimensionalization for the different boundary conditions.
	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
	In each plot, we show the PDF of the dynamics at the end of the mixedFT simulation that experienced a long rundown (green lines in Fig.~\ref{fig:rbc_scalar_comparisons}), as well as dynamics from the grey shaded region displayed in the left three panels here.
\label{fig:rbc_restart_description} }
\end{figure}

The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
It seems plausible that one should be able to take advantage of the fast evolution on display in fixedT simulations to achieve rapidly equilibrated mixedFT simulations.
The rundown in mixedFT simulations is very costly: not only do the turbulent dynamics at the large initial Rayleigh number need to be resolved (requiring more spectral modes to run the simulation), but thousands of freefall times must pass before convergence.
For a sense of scale, the first thousand freefall time units of the mixedFT case displayed in Fig.~\ref{fig:rbc_scalar_comparisons} took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours.
For comparison, the same time evolution (essentially the whole simulation) for fixedT boundary conditions took  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours.
After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
This means that at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is more than an order of magnitude larger than a fixedT simulation.

>>>>

\documentclass[aps, pre, onecolumn, nofootinbib, notitlepage, groupedaddress, amsfonts, amssymb, amsmath, longbibliography, superscriptaddress]{revtex4-1}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
\LTcapwidth=0.87\textwidth

@@

\title{Thermal relaxation is important in convective simulations: \\
on the time evolution of flows and how to avoid unnecessary thermal rundown}

@@

\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
The nature of astrophysical convection is primarily studied through the use of numerical simulations which range from studies of the highly simplified Boussinesq approximation \cite{spiegel&veronis1960} to more complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
Regardless of the degree of apparent realism of the employed simulations, numerical convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
A common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
In this model, temperature is the only thermodynamic quantity and we use the term ``mixedFT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.

Despite mixedFT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing mixedFT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``fixedT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our fixedT and mixedFT are repsectively called RB1 and RB3.}).
It is generally assumed that mixedFT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
FixedF and fixedT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that mixedFT should fall on the same scaling laws.
However, the choice of mixedFT boundaries introduces complexities into the convective system which neither fixedF or fixedT boundaries are exposed to.
First, the evolved mean temperature of a simulation with mixedFT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
Second, mixedFT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.

In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when mixedFT boundary conditions are imposed.
We also compare the flows in evolved, thermally relaxed mixedFT simulations to the flows in evolved fixedT simulations.
We find that the thermal evolution and relaxation of mixedFT systems is very long compared to fixedT systems, where it is nearly instantaneous.
However, this long thermal evolution can be bypassed by using the results of fixedT simulations as initial conditions for mixedFT simulations.
If a mixedFT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
Our results also suggest that the choice of mixedFT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to fixedT siulations.
We present these findings as follows.
In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of mixedFT systems, and then describe the asymmetries in these systems.
In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.

@@

\section{Simulation Details}
\label{sec:simulations}
We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
The equations of motion are
\begin{align}
\Div{\bm{u}} &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \sqrt{\frac{\nu}{2\Omega L_z^2}},
\end{equation}
where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency.
These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
$\Delta$ is the dimensionless temperature jump across the domain; depending on our choice of boundary condition, $\Delta$ defines either a temperature or flux Rayleigh number,
\begin{equation}
\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
\end{equation}
We study both mixedFT and fixedT thermal boundary conditions,
\begin{equation}
(\text{mixedFT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
(\text{fixedT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
\end{equation}
In the case of mixedFT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
In the case of fixedT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.

Throughout the bulk of this work, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}
The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}. 
These rotating simulations employ stress-free, impenetrable boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}

We utilize the Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \cite{burns&all2016, burns&all2019} to evolve Eqs.~(\ref{eqn:incompressible}-\ref{eqn:bouss_energy}) forward in time.
Our 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443; our 3D rotating simulations use the second-order, two-stage Runge-Kutta scheme RK222 \cite{ascher&all1997}. 
The code used to run simulations and to create the figures in this work are available publicly online in a repository of supplemental materials \cite{anders&all2020a_supp}.
Variables are time-evolved on a dealiased Chebyshev (vertical) and Fourier (horizontal, periodic) domain in which the physical grid dimensions are 3/2 the size of the coefficient grid.  
We fill $T_1$ with random white noise whose magnitude is $10^{-6}/\Peff$, and which is vertically tapered to zero at the boundaries.
We filter this noise spectrum in coefficient space, such that only the lower 25\% of the coefficients have power; this low-pass filter is used to avoid populating the highest wavenumbers with noise in order to improve the stability of our spectral timestepping methods.

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 50 freefall times of a mixedFT (orange) and a fixedT (purple) simulation.
	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the fixedT simulation.
	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the fixedT simulation (reported in appendix \ref{app:table}).
	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	The Nu vs Ra plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
	The Re vs Ra plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
	The time evolution of the mixedFT case is shown as an orange trace with the arrows showing the sense of time.
	Purple circles show our measured values of Nu in fixedT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The orange star in each plot corresponds to the fixedT case whose time evolution is shown on the left.
	Black crosses show comparison fixedT simulations as reported by ref.~\ref{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a mixedFT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a fixedT case with Ra$_{\Delta T} = 10^8$.
The mixedFT case is displayed in orange, and the fixedT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the mixedFT simulation, and this final value corresponds to the input value of the equivalent fixedT case.
On the other hand, the value of Ra$_{\partial_z T}$ for the fixedT case nearly instantaneously reaches its final value, which corresponds to the input value for the mixedFT simulation.
This discrepancy in evolution timescales, where fixedT simulations evolve quickly and mixedFT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.

In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot compensated scaling plots of Nu and Pe vs Ra$_{\Delta T}$.
Over the course of its thermal relaxation, the mixedFT case performs a sweep through Ra$_{\Delta T}$ parameter space.
During this parameter space sweep, the mixedFT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by fixedT simulations and which has been reported by previous authors.
However, we find that the value of Pe measured in the mixedFT simulation through its relaxation  is larger than the value of the Peclet number in comparison fixedT simulations until it converges to its final state.
These traces through parameter space demonstrate the importance of waiting until a mixedFT simulation has reached its equilibrated state.
During the rundown, the dynamics in mixedFT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
Both of these effects make interpretation of their results difficult until the final, equilibrated state.

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with fixedT boundary conditions and then is switched to mixedFT boundary conditions.
	The time at which we switch from fixedT to mixedFT boundaries is noted by the vertical black line.
	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
	In the fixedT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
	In the mixedFT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
	In each plot, we compare the PDF of the mixedFT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (fixedT-to-mixedFT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
\label{fig:rbc_restart_description} }
\end{figure}

The equivalence of the evolved values of Ra, Nu, and Pe in Fig.~\ref{fig:rbc_scalar_comparisons} between the mixedFT and fixedT simulations suggests that, in a volume-averaged sense, there is a comparable fixedT experiment for each mixedFT experiment.
It should therefore be possible to take advantage of the fast evolution of fixedT simulations to achieve rapidly equilibrated mixedFT simulations, which would save a great deal of computing time in solving mixedFT simulations.
The rundown in mixedFT simulations is very costly for two reasons: the turbulent dynamics at the large initial Ra$_{\Delta T}$ require more spectral modes to resolve than the equilibrated state and thousands of freefall times must pass during relaxation.
For example, for the cases displayed in Fig.~\ref{fig:rbc_scalar_comparisons}, the first thousand freefall time units took $1.43\times10^6$ iterations, or roughly $3.3 \times 10^4$ cpu-hours for the mixedFT simulation, but only  $8.4\times10^5$ iterations, or roughly $5.4\times 10^3$ cpu-hours for the fixedT simulation.
After these thousand freefall time units, the fixedT simulation has spent hundreds of freefall times in a statistically stationary relaxed state, whereas the mixedFT system continues to evolve towards its equilibrium state for an additional few thousands of time units.
Even at these modest Rayleigh numbers (Ra$_{\Delta T} = 10^8$), the cost of equilibration of a mixedFT simulation is therefore more than an order of magnitude larger than a fixedT simulation.
